---
title: "inovick_OriginalHomeworkCode_05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#First, load the packages needed:
```{r}
library(curl)
library(ggplot2)
library(gridExtra)
library(lmodel2)
```
#Then, load the data using the curl command:
```{r}
f <- curl("https://raw.githubusercontent.com/fuzzyatelin/fuzzyatelin.github.io/master/AN588_Fall21/KamilarAndCooperData.csv")
d <- read.csv(f, header = TRUE, sep = ",", stringsAsFactors = FALSE)
head(d)
```

#Challenge 1: Using the “KamilarAndCooperData.csv” dataset, run a linear regression looking at log(HomeRange_km2) in relation to log(Body_mass_female_mean) and report your β coeffiecients (slope and intercept).
```{r}
#Assigning variables:
homerange <- d$HomeRange_km2
bodymassf <- d$Body_mass_female_mean

#Using the lm function:
m <- lm(homerange ~ bodymassf)
m

#Creating a log linear regression:
logm<- lm(log(homerange) ~ log(bodymassf))
logm

logm$coefficients
#Slope= 1.036, intercept= -9.441
```

#Challenge 2: Then, use bootstrapping to sample from your data 1000 times with replacement, each time fitting the same model and calculating the same coefficients. This generates a sampling distribution for each β coefficient.
```{r}

```

##Estimate the standard error for each of your β coefficients as the standard deviation of the sampling distribution from your bootstrap and determine the 95% CI for each of your β coefficients based on the appropriate quantiles from your sampling distribution.
```{r}


```

##How does the former compare to the SE estimated from your entire dataset using the formula for standard error implemented in lm()?
```{r}

```

##How does the latter compare to the 95% CI estimated from your entire dataset?
```{r}

```
